A novell interest management algorithm for distributed simulations of MMGs

### 2008-04-30 trunk/textos/dsrt/engaoi.tex
eng

Apenas usando diferentes freqüências de atualização no gerenciamento de interesse baseado em círculo, reduziu-se em 41.59\% a largura de banda de envio utilizada em média pelo servidor por cliente. A utilização máxima de largura de banda também foi reduzida, em 36.19\%. Estes valores representam a média de redução de uso de largura de banda para os diferentes números de clientes.

No que diz respeito ao algoritmo proposto \malg, obteve-se uma redução de uso médio de largura de banda de envio de 63.51\% e 33.58\%, comparado respectivamente com o algoritmo de área de interesse circular e baseado em ângulo de visão. Reduziu-se também o pico de utilização em 52.03\% e 33.10\%, comparado com os mesmos algoritmos. Na tabela \ref{tab_summary}, são mostrados os percentuais médios de economia de largura de banda máxima e média com o algoritmo \malg, em relação aos outros algoritmos apresentados.

\begin{table}[ht]
\caption{Economia de largura de banda com o algoritmo \malg}
\centering
  \begin{tabular}{ c | c c c c }  
    \hline
   	Utilização & \noaoi & \circleaoi & \circleat & \fov \\ \hline
		Máxima	&	60.10\%	&	52.03\%	&	24.81\%	&	33.10\%	\\
		Média	&	81.64\%	&	63.51\%	&	37.48\%	&	33.58\%	\\
	\hline
  \end{tabular}
\label{tab_summary}
\end{table}

>>>>

Just by using different update frequencies with circular area based interest management, the average upload bandwidth usage by the server decreased 41.59\%. The maximum upload bandwidth usage was also reduced, decreasing 36.19\%. These values represent the average usage reduction among all different numbers of avatars, compared to the circular area of interest algorithm with no frequency update attenuation.

Regarding the proposed algorithm, \malg, it has been obtained an upload bandwidth usage reduction of 63.51\% and 33.58\%, compared to the circular area of interest and the field of view based algorithms, respectively. The maximum upload bandwidth usage was also reduced, decreasing 52.03\% and 33.10\%, compared to the same algorithms. Table \ref{tab_summary} shows the maximum and average bandwidth saving percentage of the \malg\ algorithm compared to the other techniques. For example, the maximum bandwidth utilization with \malg\ is 24.81\% less than with a circular area of interest based algorithm with update frequency attenuation.

\begin{table}[ht]
\caption{Bandwidth saving with \malg algorithm}
\centering
  \begin{tabular}{ c | c c c c }  
    \hline
   	Utilização & \noaoi & \circleaoi & \circleat & \fov \\ \hline
		Máxima	&	60.10\%	&	52.03\%	&	24.81\%	&	33.10\%	\\
		Média	&	81.64\%	&	63.51\%	&	37.48\%	&	33.58\%	\\
	\hline
  \end{tabular}
\label{tab_summary}
\end{table}
